# Codes for the Reference Soil Groups, qualifiers and specifiers

```{r}
#| echo: false

library(dplyr)
library(purrr)
library(glue)
library(stringr)
library(gt)
library(tibble)
```

## Reference Soil Groups

```{r}
#| label: tbl-sixone
#| tbl-cap: Reference Soil Groups
#| classes: no-stripe

tbl_sixone_dat <- tribble(
        ~Name, ~Code,
    'Acrisol',  'AC',
     'Alisol',  'AL',
    'Andosol',  'AN',
  'Anthrosol',  'AT',
   'Arenosol',  'AR',
   'Calcisol',  'CL',
   'Cambisol',  'CM',
    'Cryosol',  'CR',
  'Chernozem',  'CH',
    'Durisol',  'DU',
  'Ferralsol',  'FR',
   'Fluvisol',  'FL',
    'Gleysol',  'GL',
   'Gypsisol',  'GY',
   'Histosol',  'HS',
 'Kastanozem',  'KS',
   'Leptosol',  'LP',
    'Lixisol',  'LX',
    'Luvisol',  'LV',
    'Nitisol',  'NT',
   'Phaeozem',  'PH',
   'Planosol',  'PL',
 'Plinthosol',  'PT',
     'Podzol',  'PZ',
    'Regosol',  'RG',
    'Retisol',  'RT',
  'Solonchak',  'SC',
   'Solonetz',  'SN',
  'Stagnosol',  'ST',
  'Technosol',  'TC',
   'Umbrisol',  'UM',
   'Vertisol',  'VR')

tbl_sixone <- gt(tbl_sixone_dat) |>
  tab_options(
    column_labels.font.weight = 'bold',
    heading.title.font.weight = 'bold',
    table.align = 'left'
  ) |>
  tab_style(style = list(cell_text(weight = 'bold')),
            locations = cells_body(columns = 2)) 

# using interactivity to manage table length
tbl_sixone |> 
  rm_caption() |>
  opt_interactive(
    use_search = TRUE,
    use_page_size_select = TRUE
                  ) 
```

## Qualifiers

```{r}
#| label: tbl-sixtwo
#| tbl-cap: Qualifiers
#| classes: no-stripe

tbl_sixtwo_dat <- tribble(
                ~Name, ~Code,
           'Abruptic',  'ap',
             'Aceric',  'ae',
              'Acric',  'ac',
            'Acroxic',  'ao',
            'Activic',  'at',
             'Aeolic',  'ay',
         'Akrofluvic',  'kf',
      'Akromineralic',  'km',
       'Akroskeletic',  'kk',
              'Albic',  'ab',
            'Alcalic',  'ax',
               'Alic',  'al',
           'Aluandic',  'aa',
              'Andic',  'an',
         'Anthraquic',  'aq',
            'Anthric',  'ak',
       'Anthromollic',  'am',
       'Anthroumbric',  'aw',
            'Archaic',  'ah',
             'Arenic',  'ar',
         'Arenicolic',  'ad',
         'Areninovic',  'aj',
          'Argisodic',  'as',
               'Aric',  'ai',
              'Arzic',  'az',
         'Biocrustic',  'bc',
             'Brunic',  'br',
              'Bryic',  'by',
           'Calcaric',  'ca',
             'Calcic',  'cc',
       'Calcifractic',  'cf',
             'Cambic',  'cm',
         'Capillaric',  'cp',
             'Carbic',  'cb',
         'Carbonatic',  'cn',
           'Carbonic',  'cx',
            'Chernic',  'ch',
             'Claric',  'cq',
          'Chloridic',  'cl',
            'Chromic',  'cr',
             'Clayic',  'ce',
         'Clayinovic',  'cj',
            'Coarsic',  'cs',
            'Cohesic',  'co',
           'Columnic',  'cu',
             'Cordic',  'cd',
              'Cryic',  'cy',
            'Cutanic',  'ct',
             'Densic',  'dn',
        'Differentic',  'df',
          'Dolomitic',  'do',
             'Dorsic',  'ds',
            'Drainic',  'dr',
              'Duric',  'du',
            'Dystric',  'dy',
     'Ejectiskeletic',  'jk',
            'Ekranic',  'ek',
              'Endic',  'ed',
              'Entic',  'et',
               'Epic',  'ep',
            'Escalic',  'ec',
             'Eutric',  'eu',
         'Eutrosilic',  'es',
       'Evapocrustic',  'ev',
           'Ferralic',  'fl',
             'Ferric',  'fr',
           'Ferritic',  'fe',
             'Fibric',  'fi',
            'Floatic',  'ft',
             'Fluvic',  'fv',
              'Folic',  'fo',
            'Fractic',  'fc',
     'Fractiskeletic',  'fk',
             'Fragic',  'fg',
             'Garbic',  'ga',
              'Gelic',  'ge',
        'Gelistagnic',  'gt',
        'Geoabruptic',  'go',
              'Geric',  'gr',
            'Gibbsic',  'gi',
            'Gilgaic',  'gg',
             'Glacic',  'gc',
             'Gleyic',  'gl',
            'Glossic',  'gs',
          'Greyzemic',  'gz',
             'Grumic',  'gm',
             'Gypsic',  'gy',
       'Gypsifractic',  'gf',
           'Gypsiric',  'gp',
             'Haplic',  'ha',
              'Hemic',  'hm',
             'Histic',  'hi',
             'Hortic',  'ht',
              'Humic',  'hu',
          'Hydragric',  'hg',
             'Hydric',  'hy',
        'Hydrophobic',  'hf',
          'Hyperalic',  'jl',
    'Hyperartefactic',  'ja',
        'Hypercalcic',  'jc',
         'Hyperduric',  'ju',
       'Hyperdystric',  'jd',
        'Hypereutric',  'je',
      'Hyperferritic',  'jf',
        'Hypergarbic',  'jb',
         'Hypergeric',  'jq',
        'Hypergypsic',  'jg',
         'Hyperhumic',  'jh',
     'Hyperhydragric',  'jy',
      'Hypermagnesic',  'jm',
        'Hypernatric',  'jn',
       'Hyperorganic',  'jo',
         'Hypersalic',  'jz',
     'Hypersideralic',  'jr',
        'Hyperspodic',  'jp',
        'Hyperspolic',  'jj',
      'Hypersulfidic',  'js',
       'Hypertechnic',  'jt',
       'Hyperthionic',  'ji',
         'Hyperurbic',  'jx',
       'Hyposulfidic',  'ws',
        'Hypothionic',  'wi',
           'Immissic',  'im',
           'Inclinic',  'ic',
      'Inclinigleyic',  'iy',
     'Inclinistagnic',  'iw',
         'Infraandic',  'ia',
        'Infraspodic',  'ia',
           'Irragric',  'ir',
           'Isolatic',  'il',
          'Isopteric',  'ip',
             'Kalaic',  'ka',
           'Lamellic',  'll',
           'Lapiadic',  'ld',
              'Laxic',  'la',
             'Leptic',  'le',
             'Lignic',  'lg',
             'Limnic',  'lm',
            'Limonic',  'ln',
              'Linic',  'lc',
             'Lithic',  'li',
         'Litholinic',  'lh',
              'Lixic',  'lx',
             'Loamic',  'lo',
         'Loaminovic',  'lj',
              'Luvic',  'lv',
           'Magnesic',  'mg',
      'Manganiferric',  'mf',
              'Mahic',  'ma',
              'Mawic',  'mw',
              'Mazic',  'mz',
          'Mineralic',  'mi',
       'Minerolimnic',  'ml',
           'Mochipic',  'mc',
             'Mollic',  'mo',
             'Mulmic',  'mm',
            'Murshic',  'mh',
             'Muusic',  'mu',
            'Naramic',  'nr',
             'Natric',  'na',
             'Nechic',  'ne',
          'Neobrunic',  'nb',
          'Neocambic',  'nc',
              'Nitic',  'ni',
              'Novic',  'nv',
          'Nudiargic',  'ng',
         'Nudilithic',  'nt',
         'Nudinatric',  'nn',
         'Nudipetric',  'np',
         'Nudiyermic',  'ny',
             'Ochric',  'oh',
        'Oligoeutric',  'ol',
             'Ombric',  'om',
       'Organolimnic',  'oo',
  'Organotransportic',  'ot',
           'Ornithic',  'oc',
       'Orthodystric',  'od',
        'Orthoeutric',  'oe',
        'Orthofluvic',  'of',
     'Orthomineralic',  'oi',
      'Orthoskeletic',  'ok',
         'Ortsteinic',  'os',
           'Oxyaquic',  'oa',
          'Oxygleyic',  'oy',
             'Pachic',  'ph',
            'Panpaic',  'pb',
         'Paviyermic',  'vy',
             'Pellic',  'pe',
        'Pelocrustic',  'pq',
             'Petric',  'pt',
        'Petrocalcic',  'pc',
         'Petroduric',  'pd',
        'Petrogypsic',  'pg',
      'Petroplinthic',  'pp',
         'Petrosalic',  'ps',
       'Pisoplinthic',  'px',
             'Placic',  'pi',
            'Plaggic',  'pa',
           'Plinthic',  'pl',
              'Posic',  'po',
             'Pretic',  'pk',
          'Profondic',  'pn',
      'Profundihumic',  'dh',
             'Protic',  'pr',
         'Protoandic',  'qa',
         'Protoargic',  'qg',
        'Protocalcic',  'qc',
        'Protogleyic',  'qy',
        'Protogypsic',  'qq',
        'Protokalaic',  'qk',
         'Protosalic',  'qz',
         'Protosodic',  'qs',
        'Protospodic',  'qp',
       'Protostagnic',  'qw',
       'Prototechnic',  'qt',
       'Prototephric',  'qf',
        'Protovertic',  'qv',
             'Puffic',  'pu', 
              'Pyric',  'py', 
         'Radiotoxic',  'rx', 
             'Raptic',  'rp', 
        'Reductaquic',  'ra', 
           'Reductic',  'rd', 
      'Reductigleyic',  'ry',
      'Relictigleyic',  'rl', 
     'Relictistagnic',  'rw',
      'Relictiturbic',  'rb', 
          'Relocatic',  'rc', 
            'Rendzic',  'rz', 
              'Retic',  'rt', 
              'Rheic',  'rh', 
             'Rhodic',  'ro', 
             'Rockic',  'rk', 
              'Rubic',  'ru', 
             'Rustic',  'rs', 
              'Salic',  'sz', 
             'Sapric',  'sa', 
        'Saporlithic',  'sh', 
          'Sideralic',  'se', 
           'Silandic',  'sn', 
             'Siltic',  'sl', 
         'Siltinovic',  'sj', 
           'Skeletic',  'sk', 
       'Skeletofolic',  'ko', 
      'Skeletohistic',  'kh',
 'Skeletotransportic',  'kt', 
              'Sodic',  'so', 
          'Solimovic',  'sv', 
            'Sombric',  'sb', 
            'Someric',  'si', 
       'Somerimollic',  'sm', 
      'Somerirendzic',  'sr', 
       'Someriumbric',  'sw',
             'Spodic',  'sd',
             'Spolic',  'sp',
            'Stagnic',  'st',
         'Subaquatic',  'sq',
           'Sulfatic',  'su',
           'Sulfidic',  'sf',
            'Takyric',  'ty',
            'Technic',  'te',
      'Technotephric',  'tt',
            'Tephric',  'tf',
             'Terric',  'tr',
            'Thionic',  'ti',
        'Thixotropic',  'tp',
             'Thyric',  'th',
            'Tidalic',  'td',
            'Tonguic',  'to',
      'Tonguichernic',  'tc',
       'Tonguimollic',  'tm',
       'Tonguiumbric',  'tw',
       'Totilamellic',  'ta',
              'Toxic',  'tx',
        'Transportic',  'tn',
           'Tsitelic',  'ts',
             'Turbic',  'tu',
             'Umbric',  'um',
              'Urbic',  'ub',
           'Uterquic',  'uq',
             'Vermic',  'vm',
             'Vertic',  'vr',
             'Vitric',  'vi',
             'Wapnic',  'wa',
            'Xanthic',  'xa',
             'Yermic',  'ye')

tbl_sixtwo <- gt(tbl_sixtwo_dat) |>
  tab_options(
    column_labels.font.weight = 'bold',
    heading.title.font.weight     = 'bold',
    table.align = 'left'
  ) |>
  tab_style(style = list(cell_text(weight = 'bold')),
            locations = cells_body(columns = 2))

# using interactivity to manage table length
tbl_sixtwo |> 
  opt_interactive(
    use_search = TRUE,
    use_page_size_select = TRUE
                  ) |>
  rm_caption()
```

## Specifiers

```{r}
#| label: tbl-sixthree
#| tbl-cap: Specifiers
#| classes: no-stripe

tbl_sixthree_dat <- 
  tribble(
    ~Name, ~Code,
    'Amphi',  '..m',
    'Ano',    '..a',
    'Bathy',  '..d',
    'Endo',   '..n',
    'Epi',    '..p',
    'Kato',   '..k',
    'Panto',  '..e',
    'Poly',   '..y',
    'Supra',  '..s',
    'Thapto', '..b'
  )

tbl_sixthree <- gt(tbl_sixthree_dat) |>
  tab_options(
    column_labels.font.weight = 'bold',
    heading.title.font.weight     = 'bold',
    table.align = 'left'
  ) |>
  tab_style(style = list(cell_text(weight = 'bold')),
            locations = cells_body(columns = 2)) |>
  cols_width(Code ~ pct(20))

tbl_sixthree
```

## Combinations with the Novic qualifier

::: callout-note
See Chapter 2.4, [Buried soils](chapter-02.qmd#sec-buried)
:::

```{r}
#| label: tbl-sixfour
#| tbl-cap: Novic combinations
#| classes: no-stripe

tbl_sixfour_dat <- 
  tribble(
    ~Name, ~Code,
    'Aeoli-novic',      'nva',
    'Fluvi-novic',      'nvf',
    'Solimovic-novic',  'nvs',
    'Techni-novic',     'nvt',
    'Tephri-novic',     'nvv',
    'Transporti-novic', 'nvp'
  )

tbl_sixfour <- gt(tbl_sixfour_dat) |>
  tab_options(
    column_labels.font.weight = 'bold',
    heading.title.font.weight     = 'bold',
    table.align = 'left'
  ) |>
  tab_style(style = list(cell_text(weight = 'bold')),
            locations = cells_body(columns = 2)) |>
  cols_width(Code ~ pct(20))

tbl_sixfour
```

**Note:** The codes for the combinations with subqualifiers of the [Novic](chapter-05.qmd#sec-nv) qualifier are constructed accordingly, e.g., Aeoli-Siltinovic (sja).

### Rules for the use of the codes for naming soils

At the first level of classification, the code of the RSG stands alone.

At the second level, the code starts with the RSG,\
followed by a '-',\
followed by the principal qualifiers, if several ones apply, with a '.' between them, according to the list from top to bottom,\
if applicable, followed by a '-',\
followed by the supplementary qualifiers related to texture, if several ones apply, with a '.' between them, in the sequence from the top to the bottom of the profile,\
if applicable, followed by a '-',\
followed by the other supplementary qualifiers, if several ones apply, with a '.' in between them, in alphabetical order of the qualifier names (not in alphabetical order of their codes),\
if applicable, followed by a '-',\
followed by qualifiers that are not in the list for the particular RSG.

Subqualifiers (qualifiers combined with specifiers) are placed in the order of the qualifiers as if they were used without the specifier. Exception: If used with a principal qualifier, the Proto-, Bathy- and Thapto- subqualifiers must shift to the supplementary qualifiers,

If one group of qualifiers is empty, the '-' is still included, if one of the following groups is not empty.

The resulting scheme is as follows:\
RSG{-}\[PQ1\[.PQ2\]etc\]{-}\[TQ1\[.TQ2\]etc\]{-}\[SQ1\[.SQ2\]etc\]{-}\[NQ1\[.NQ2\]etc\]

With: PQ = principal qualifier, with or without added specifiers, TQ = supplementary qualifier related to texture, with or without added specifiers, SQ = other supplementary qualifier, with or without added specifiers, NQ = qualifier not listed for the particular RSG, with or without added specifiers; etc = further qualifiers can be added in the same way if necessary; elements in \[\] are listed if they apply; elements in {} are necessary if elements follow.

### Examples of the use of the codes for naming soils

Albic Stagnic Luvisol (Episiltic, Katoclayic, Bathysiltic, Cutanic, Differentic, Epic, Ochric):\
LV-st.ab-slp.cek.sld-ct.df.ep.oh

Hemic Folic Endorockic Histosol (Dystric):\
HS-rkn.fo.hm-dy

Haplic Ferralsol (Pantoloamic, Dystric, Endic, Humic, Bathypetroplinthic, Posic):\
FR-ha-loe-dy.ed.hu.ppd.po

Calcaric Skeletic Pantofluvic Fluvisol (Pantoarenic, Ochric):\
FL-fve.sk.ca-are-oh

Dystric Umbric Aluandic Andosol (Pantosiltic, Thaptohistic, Hyperhumic):\
AN-aa.um.dy-sle-hib.jh

Isolatic Ekranic Technosol (Supraarenic, Supracalcaric):\
TC-ek.il-ars-cas

Dystric Arenosol (Bathyspodic):\
AR-dy-sdd

### Rules for the use of the codes for creating map legends

At the first scale level, the code of the RSG stands alone.\
At the second and third scale level, the code starts with the RSG,\
followed by a '-',\
followed by the principal qualifiers (number according to the scale level) according to the list from top to bottom, with a '.' between them.

If elective qualifiers are added,\
a '-' is added,\
followed by the elective qualifiers, with a '.' between them (the principal qualifiers are placed first, and of them, the first applicable qualifier is placed first, and the sequence of any supplementary qualifiers added is decided by the soil scientist who makes the map).

If according to the scale level no principal qualifier has to be added, the '-' is still included, if any elective qualifier is added.

If codominant or associated soils are indicated, the words 'dominant:', 'codominant:' and 'associated:' are written before the code of the soil.

The resulting scheme is as follows:\
RSG{-}\[PQ1\[.PQ2\]\]{-}\[EQ1\[.EQ2\]etc\]

With: PQ = principal qualifier, EQ = elective qualifier; etc = further qualifiers can be added in the same way if necessary; elements in \[\] are listed if they apply; elements in {} are necessary if elements follow.

### Examples of the use of the codes for creating map legends

Umbric Geric Xanthic Ferralsols (Clayic, Dystric, Endic, Humic):\
first scale level: FR\
second scale level: FR-xa\
third scale level: FR-xa.gr

If elective qualifiers are added: examples:\
first scale level: FR--ce\
second scale level: FR-xa-ce\
third scale level: FR-xa.gr-um.ce.dy

